
```{r}
source('R/packages.R')
source('R/functions.R')
source('R/functions-phase2.R')
source('R/tables-phase2.R')
source('R/tables.R')

```



```{r  load-data-50155}
my_site <- 50155
```


`r paste0('## Crossing ', my_site, ' - ', my_overview_info() %>% pull(road_name), ' - ', my_overview_info() %>% pull(stream_name))`


### Site Location

Crossing `r as.character(my_site)` is located on a `r my_pscis_info() %>% pull(stream_name)`, approximately 75m upstream from the confluence with Lizard Creek. The stream is located approximately 100m east of the location where it is mapped on the freshwater atlas stream layer.


<br>

### Background

At the crossing location, the stream is 2nd order with a watershed area upstream of the road of approximately 1.8km^2^. The elevation of the watershed ranges from a maximum of 1945m to 1080m at the culvert. One 12m long bridge (PSCIS 197543) is located upstream of the subject crossing approximately 575m on the Lazy Lizard bike trail wht another 7m long bridge structure located downstream also on a recreational trail. Provincial records indicate that there is no fisheries information available for the stream [@moeStreamInventorySample].

<br>

PSCIS stream crossing `r as.character(my_site)` was ranked as a high priority for follow up with habitat confirmation due to the relatively large size of the stream, previously rated high value habitat and because it was prioritized for follow up by @vastresourcesolutionsinc.2012FishPassage2013. The habitat confirmation was completed on `r my_pscis_info() %>% pull(date) %>% format(., format = "%B %d, %Y")`. A map of the watershed including areas surveyed is provided in Attachment 1 – Map [`r my_bcfishpass() %>% pull(map_tile_display_name)`](`r my_mapsheet()`).

<br>

### Stream Characteristics at Crossing

At the time of the survey, the un-embedded and non-backwatered `r my_pscis_info() %>% pull(diameter_or_span_meters)`m diameter crossing was considered a barrier to upstream fish passage with a pipe length of `r my_pscis_info() %>% pull(length_or_width_meters)`m, a culvert slope of `r my_pscis_info() %>% pull(culvert_slope_percent)`%, a stream width ratio of `r my_pscis_info() %>% pull(stream_width_ratio)` an outlet drop of `r my_pscis_info() %>% pull(outlet_drop_meters)`m (Table \@ref(tab:tableculvert-50155). Water temperature was `r my_habitat_info() %>% filter(rowname == 'temperature c') %>% pull(us)`$^\circ$C, pH was `r my_habitat_info() %>% filter(rowname == 'p h') %>% pull(us)` and conductivity was `r my_habitat_info() %>% filter(rowname == 'conductivity m s cm') %>% pull(us)`uS/cm.

<br>



```{r tableculvert-50155}
make_tab_summary(df = pscis2 %>% filter(pscis_crossing_id == my_site)) %>% 
  kable() %>% 
  kableExtra::add_footnote(label = paste0('Comments: ', pscis2 %>% filter(pscis_crossing_id == my_site) %>% pull(assessment_comment)), notation = 'none') %>% #this grabs the comments out
  kableExtra::add_footnote(label = paste0('Photos: ', 
                                          paste0('![](https://github.com/NewGraphEnvironment/', basename(getwd()), '/raw/master/data/photos/', my_site, '/crossing_all.JPG)')), notation = 'none')
```


